\documentclass[a4paper, landscape]{article}

\input{include/cardLibs.tex}
\input{include/cardColours.tex}
\input{include/cardStyles.tex}

\begin{document}
\pagestyle{empty}
\begin{center}

\greycard{Private Eye}{Elementary, my dear Watson.}{
	At the end of the game, before anyone else reveals their cards, you must
	publicly announce the identity of the buried card. If correct, you win.
	If incorrect, you lose.
}
\greycard{Gambler}{It's all or nothing}{
	Before the last round begins, you must publically announce which team
	you think is going to win. If you are correct, you win. If not, you
	lose.
} 
\greycard{Hot Potato}{Hot, hot, hot!!!}{
	You lose at the end of the game
	\\\vspace{0.5cm} 
	Any player that card shares or color shares with you must immediately
	trade cards with you: You gain their card, and assume their previous
	role. The other player becomes the Hot Potato.
} 
\greycard{Anarchist}{Some people just want to watch the world burn.}{
	You win if you helped overthrow a \character{Leader} in the majority of
	rounds.
}
\greycard{Minion}{Master must always lead!}{
	You win if a \character{Leader} is never overthrown in the same room as
	you.
}
\greycard {Mastermind} {There's no place like evil lair.} {
	You win if you are a room's leader at the end of the game AND you were
	the leader of the opposing room at some point during the game.
}
\greycard {MI6} {The name's Bond.} {
	You win if you card share with the Bomber and the President before the
	end of the game.
}
\greycard {Nuclear Tyrant} {} {
	At the end of the game, you are asked if you shared your card with both
	the \character{President} and the \character{Bomber}. You win if the
	\character{President} and the \character{Bomber} did not card share
	with you by the end of the game. If you win, all other players lose.
	\\\vspace{0.25cm}
	You begin with the "foolish" condition. Players with the "foolish"
	condition can never turn down an offer to card share. "foolish" + "shy"
	and "foolish" + "coy" cancel each other out.
}

\backpanel
\newpage

\greycard{Telepath}{See into the future...}{
	Before the last hostage exchange (during the final round), you must
	publically announce that you are the \character{Telepath} and predict
	which player is coming into your current room. You win if you are
	correct.
}
\purplecard{Amnesiac}{Whose team am I on again???}{
	At the end of the game, before anyone else reveals their cards, you must
	declare which team you are on by saying, ``I remember which team I am
	on. I am on team ...''. Choosing either: The blue team, the red team, or
	nobody's team. If you choose the team with a minority of players (or
	picked nobody's team in case of a tie), you win.
}
\greycard {Agoraphobe} {I'll stay inside, thanks.} {
	You win as long as you never leave your inital room.
}
\greycard {Traveler} {Oh, the places you'll go!} {
	You win if you are sent to a different room as a hostage at the end of
	MOST rounds. For example, in a 3 round game, you must change rooms
	2 times to win.
}
\purplecard{Drunk}{I'm not slurring... ur slurrrr}{
	At the beginning of the last round of the game, the \character{Drunk}
	should trade their card with the "sober" card.  Assume all powers and
	responsibilities associated with the "sober" character card. You lose
	if you forget or are unable to trade your card for the "sober" card.\\
	\vspace{0.1cm} 
	Note: the "sober" card is cleansed, so it has no conditions (shy, coy,
	etc.) when you pick it up.
}
\purplecard{Leprechaun}{Me Lucky Charms!}{
	At the end of the game, the \character{Leprechaun} wins.\\
	\vspace{0.1cm}
	You begin with the "foolish" condition. Players with the "foolish"
	condition can never turn down an offer to card or color share. Any time
	the \character{Leprechaun} shares cards or colors with another player,
	the two players swap cards, roles, allegiances, and powers. A player
	can only ever be the \character{Leprechaun} once per game. 
}
\purplecard{Zombie}{Brains...}{
	You begin with the "zombie" condition. Players who have the "zombie"
	condition are now on Team Zombie. Team Zombie wins if all players who
	are not "dead" at the end of the game are on Team Zombie. Any player
	that card or color shares with a player with the "zombie" condition
	gains the "zombie" condition. Let them know by whispering "I'm a
	zombie, and now so are you".
}

\backpanel

\end{center}
\end{document}
